---
title: Landlords technical reports
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE)
```

First lets set up our libraries and import our data with our processing pipeline:

```{r, "imports", message = FALSE}
source("init.R")
```

```{r, "import data"}
llr_joined = import_llr() %>% process_llr() %>% join_llr()
```
First we import the data, process it, then join it. The final function adds a new, joined, dataset called ct_merged to our list of dataframes.

ct_merged is the join of three datasets. ``Housing Benefit``, ``Council Tax`` and ``Landlord's register``.

**investigating the datasets**

Firstly I'm going to clone the ct_merged data frame into its own variable for ease of use:
```{r clone_merged}
ct_merged = llr_joined$ct_merged

```

The joined dataset uses council tax as its baseline (its the largest of the lot), but horizontally the landlords register and housing benefits. part of the ``process_llr()`` script prepends the column names with a label to make it easier to identify them later.

```{r ct_colnames}
colnames(ct_merged)
```

**Unmatched records** 

We've merged the three datasets here using a *UPRN* - Unique Property Reference Number - which is the defacto way to identify physical properties in the UK. We don't have UPRN's for all CT, HB and LLR records, so not all get joined. 

The numbers below are the percentages of records we DON'T have UPRN's for. 

```{r uprn_coverage}
### Landlords registrations that we can't link to CTAX / Benefits via UPRN - 6,510 / 55,753 = 11.7%
round(llr_joined$llr %>% filter(!(uid_full %in% llr_joined$ct_merged$llr_uid)) %>% nrow() / nrow(llr_joined$llr), 2) 

### Ctax records that we don't have a uprn for - 3499 / 307,422 = 1.1%
round(llr_joined$ct %>% filter(!(property_ref %in% llr_joined$finref_uprn$FIN_REF)) %>% nrow() / nrow(llr_joined$ct),2)

### Benefits records that we don't have a uprn for - 1,218 / 98,359 = 1.2%
round(llr_joined$benefits %>% filter(!(property_ref %in% llr_joined$finref_uprn$FIN_REF)) %>% nrow() / nrow(llr_joined$benefits),2)
```

Pretty good coverage for council tax and housing benefit - but not so much with the LLR. We'll see later the impact this has on our overall assumptions and results.

**Estimating tenure from council tax and housing benefit**

We established a number of rules to estimate tenure  
```{r tenure_estimate}


```
